\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
Josh conclusion

 \section{Contribution and Outlook}
 We contribute a model, \systemEnding, that learns to program by
 bootstrapping a DSL with new domain-specific primitives that the algorithm itself discovers.
  Alongside this DSL, we train a bottom-up
 neural recognition model that learns how to efficiently deploy the
 DSL and hone in on the right programs.
 We believe that this
 integration of top-down symbolic representation and bottom-up neural
 networks -- both of them learned -- is a useful general approach for
 program induction.
Many directions remain open for future work. Two immediate goals are to
integrate more sophisticated neural recognition models~\cite{devlin2017robustfill} and
program synthesizers~\cite{solar2008program}, which may improve performance in some
domains over the generic methods used here, and to explore DSL
meta-learning: Can we find a single universal primitive set that could
effectively bootstrap DSLs for new domains, including the four domains
considered but also many others?

\bibliography{main}
\bibliographystyle{icml2018}

>>>>

 \section{Contribution and Outlook}
\system learns to program by bootstrapping a DSL with new
domain-specific primitives that the algorithm itself discovers,
together with a neural recognition model that learns how to
efficiently deploy the DSL on new tasks. We believe this integration
of top-down symbolic representations and bottom-up neural networks --
both of them learned -- could help make program induction systems more
generally useful for AI. Many directions remain open. Two immediate
goals 
are to integrate more sophisticated neural recognition
models~\cite{devlin2017robustfill} and program
synthesizers~\cite{solar2008program}, which may improve performance in
some domains over the generic methods used here, and to
explore DSL meta-learning: Can we find a \emph{single} universal
primitive set that could effectively bootstrap DSLs for new domains,
including the four domains considered but many others?
\bibliography{main}
\bibliographystyle{icml2018}
